\Large\textbf{Surrogate Regret Bounds for Polyhedral Losses}

### 2021-12-03 rates-neurips-21/neurips-poster/main.tex
final poster

\begin{frame}{~}{}
  \vskip-1em
  \centerline{\includegraphics[width=0.65\linewidth]{figs/hinge}}
  \vskip1em

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{~}{}
  Desirable surrogates:
  \begin{itemize}
    \item Optimizable.  \hintright{Convex, strongly convex, etc.}
    \item Generalization bound, convergence rate.
%  \textbf{2.} Generalization bound; convergence rate. \\
%  \hint{e.g. with $n$ data points, $\Reg_L(h;\D) \leq O(\sqrt{1/n})$.}
    \item \textbf{Connection to \redem{target}...}
  \end{itemize}

  \vskip1em
  \textbf{Regret transfer function} (\emph{calibration function}) $\zeta: \reals_{\geq 0} \to \reals_{\geq 0}$:  \hintright{continuous at zero, $\zeta(0) = 0$}

@@

  \pause
  \vskip1em
  If \textbf{any such $\zeta$} exists, $(L,\psi)$ is \textbf{consistent} for $\ell$.  \\
  \hint{As $\Reg_L(h^{(n)}; \D) \to 0$, we have $\Reg_{\ell}^{(n)}(\psi \circ h^{(n)} ; \D) \to 0$.}

@@

  \vskip1em
  \pause
  Prior work: binary classification (Zhang et al. 2004, etc.); bipartite ranking (Agarwal 2014, etc.); multiclass classification (Duchi et al. 2018, etc.); hierarchical classification (Ramaswamy et al. 2015); strongly convex surrogates (Nowak-Vila et al. 2019, etc.).
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Results}{}
  \begin{block}{Theorem 1}
    Suppose $L$ is polyhedral and $(L,\psi)$ are consistent for the discrete target $\ell$.
    Then there exists $C > 0$ such that, for all $\D$ and $h$,
    \[ \Reg_{\ell}(\psi \circ h; \D) \leq C \cdot \Reg_L(h; \D) . \]
  \end{block}

  \pause
  \vskip1em
  \emph{Proof sketch.}
  Fix $x$; let $p,q \in \simplex$ be distributions of $y$ given $x$.
  \begin{itemize}[<+->]
    \item Suffices to prove that for all $p$ and $u$, $\Reg_{\ell}(\psi(u);p) \leq C \cdot \Reg_L(u;p)$.
    \item $\forall q$, $\exists \alpha_q > 0$ such that $\Reg_{\ell}(\psi(u); q) \leq \alpha_q \cdot \Reg_L(u; q)$.
    \item Polyhedral losses have a \textbf{finite structure}: \hintright{related to embeddings framework}
    \begin{itemize}
      \item There is a finite $U \subseteq \reals^d$ such that, for all $p$, $U$ contains an optimal prediction.
      \item These $U$ partition $\simplex$ into finitely many polytopes.
    \end{itemize}
    \item Regret is linear on each polytope.
    \item Therefore $\Reg_L(u ; p)$ is a convex combination over the corners.
    \item So we can take $C = \max_{\text{corners $q$}} \alpha_q$.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{~}{}
  \begin{block}{Theorem 2}
    Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
    Suppose $(L,\psi)$ is consistent for $\ell$ with:
    \[  \Reg_{\ell}(\psi \circ h) \leq \zeta\Big( \Reg_L(h) \Big) . \]
   Then there exists $c > 0$ such that, for all small enough $\epsilon > 0$,
    \[ \zeta(\epsilon) \geq c \sqrt{\epsilon} . \]
  \end{block}

>>>>

\begin{frame}{~}{}
  \vskip-2pt
  \centerline{\includegraphics[width=0.65\linewidth]{figs/hinge}}
  \vskip1em

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{frame}{~}{}
  \begin{columns}
    \begin{column}{0.24\linewidth}
      \vskip-1pt
      Desirable surrogates:
    \end{column}
    \begin{column}{0.73\linewidth}
      \vskip-20pt
      \begin{itemize}
      \item Optimizable.  \hintright{Convex, strongly convex, etc.}
      \item Generalization bound, convergence rate.
        % \textbf{2.} Generalization bound; convergence rate. \\
        % \hint{e.g. with $n$ data points, $\Reg_L(h;\D) \leq O(\sqrt{1/n})$.}
      \item \textbf{Connection to \redem{target}...}
      \end{itemize}
    \end{column}
  \end{columns}

  \vskip15pt
  \textbf{Regret transfer function} $\zeta: \reals_{\geq 0} \to \reals_{\geq 0}$:  \hintright{Continuous at $0$, $\zeta(0) = 0$}

@@

  \pause
  If \textbf{any such $\zeta$} exists, $(L,\psi)$ is \textbf{consistent} for $\ell$.  \\
  \hint{As $\Reg_L(h^{(n)}; \D) \to 0$, we have $\Reg_{\ell}^{(n)}(\psi \circ h^{(n)} ; \D) \to 0$.}

@@

  \vskip15pt
  \pause
  Prior work: binary classification (Zhang et al. 2004, etc.); bipartite ranking (Agarwal 2014, etc.); multiclass classification (Duchi et al. 2018, etc.); hierarchical classification (Ramaswamy et al. 2015); strongly convex surrogates (Nowak-Vila et al. 2019, etc.).
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{frame}{Results}{}
  {\vspace*{-3ex}}
  \begin{block}{\vspace*{-3ex}}
    \textbf{Theorem 1.}~
    Suppose $L$ is polyhedral and $(L,\psi)$ are consistent for the discrete target $\ell$.
    Then there exists $C > 0$ such that, for all $\D$ and $h$,
    \[ \Reg_{\ell}(\psi \circ h; \D) \leq C \cdot \Reg_L(h; \D) . \]
  \end{block}

  \smallskip
  \emph{Proof sketch.}
  Fix $x$; let $p,q \in \simplex$ be distributions of $y$ given $x$.
  \begin{itemize}[<+->]
  \item Suffices to prove that for all $p$ and $u$, $\Reg_{\ell}(\psi(u);p) \leq C \cdot \Reg_L(u;p)$.
  \item $\forall q$, $\exists \alpha_q > 0$ such that $\Reg_{\ell}(\psi(u); q) \leq \alpha_q \cdot \Reg_L(u; q)$.
  \item Polyhedral losses have a \textbf{finite structure}: \hintright{related to embeddings framework}
    \begin{itemize}
    \item There is a finite $U \subseteq \reals^d$ such that, for all $p$, $U$ contains an optimal prediction.
    \item These $U$ partition $\simplex$ into finitely many polytopes.
    \end{itemize}
  \item Regret is linear on each polytope.
  \item Therefore $\Reg_L(u ; p)$ is a convex combination over the corners.
  \item So we can take $C = \max_{\text{corners $q$}} \alpha_q$.
  \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{frame}{~}{}
  {\vspace*{-3ex}}
  \begin{block}{\vspace*{-3ex}}
    \textbf{Theorem 2.}~
    Let $L$ be a locally strongly convex surrogate with locally Lipschitz gradient.
    Suppose $(L,\psi)$ is consistent for $\ell$ with:
    \[  \Reg_{\ell}(\psi \circ h) \leq \zeta\Big( \Reg_L(h) \Big) . \]
    Then there exists $c > 0$ such that, for all small enough $\epsilon > 0$,
    \[ \zeta(\epsilon) \geq c \sqrt{\epsilon} . \]
  \end{block}
